\documentclass[25pt, a0paper, portrait]{tikzposter}

% Encodage et typographie
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[french,english]{babel}
\usepackage{lmodern}
\usepackage{amsmath, amssymb, amsfonts, dsfont}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,positioning,fit,backgrounds,calc}

% 1. Définition des couleurs officielles (extraites de polytechnique.sty)
\definecolor{bleu303}{RGB}{0,62,92}
\definecolor{bleu315}{RGB}{0,104,128}
\definecolor{rouge485}{RGB}{213,43,30}
\definecolor{bleu303pale}{RGB}{204,216,222} % Approximation de bleu303!20!white

% 2. Création d'un style de couleur personnalisé pour tikzposter
\definecolorstyle{PolyColors}{
    \definecolor{colorOne}{named}{bleu303}
    \definecolor{colorTwo}{named}{bleu315}
    \definecolor{colorThree}{named}{rouge485}
}{
    % Arrière-plan (fond clair pour la lisibilité)
    \colorlet{backgroundcolor}{bleu303pale!30!white}
    \colorlet{framecolor}{bleu303}
    %
    % En-tête (Titre)
    \colorlet{titlebgcolor}{bleu303}
    \colorlet{titlefgcolor}{white}
    %
    % Blocs principaux
    \colorlet{blocktitlebgcolor}{bleu303}
    \colorlet{blocktitlefgcolor}{white}
    \colorlet{blockbodybgcolor}{white}
    \colorlet{blockbodyfgcolor}{black}
    %
    % Sous-blocs (Inner blocks)
    \colorlet{innerblocktitlebgcolor}{bleu315}
    \colorlet{innerblocktitlefgcolor}{white}
    \colorlet{innerblockbodybgcolor}{bleu315!10!white}
    \colorlet{innerblockbodyfgcolor}{black}
    %
    % Notes (Post-its)
    \colorlet{notefgcolor}{black}
    \colorlet{notebgcolor}{rouge485!20!white}
    \colorlet{notefrcolor}{rouge485}
}

% 3. Application du thème Desert combiné avec nos couleurs
\usetheme{Desert}
\usecolorstyle{PolyColors}

% 4. Informations du document
\title{\parbox{\linewidth}{\centering \textbf{AudioConditioner}\\[0.3em] \Large Applications}}
\author{Keyvan Attarian \& Baptiste Arnaudo}
\institute{CSC\_52002\_EP - Multimodal generative AI}


\begin{document}

\maketitle

\begin{columns}

\column{0.5}

\block{\MakeUppercase{Application I: Image to Ambient Music}}{
    One direct and powerful application of the \textbf{Audio\-Conditioner} framework is generating ambient music and atmospheres based solely on visual inputs. By passing an image into our pipeline:
    \vspace{0.5cm}
    
    \begin{itemize}
        \item The \textbf{BLIP Model} automatically captions the image's scene, extracting emotional elements, colors, objects, and implicit narrative.
        \item This scene description drives the \textbf{Audio\-Conditioner} pipeline (through the \textbf{CLAP Descriptor} and \textbf{Stable Audio}), outputting high-fidelity audio that perfectly encapsulates the mood of the image.
        \item The audio candidates are re-ranked using the \textbf{CLAP Cosine Similarity Filter} to ensure the highest alignment with the initial visual.
    \end{itemize}
    \vspace{0.5cm}
    This enables seamless soundtrack generation for static artwork, game environments, or visual media.
}

\block{\MakeUppercase{Application II: Text Reading with Adaptive Music}}{
    The \textbf{ReadMusic} module merges Speech Synthesis with adaptive background music scoring, turning textual narratives into fully immersive audiobooks.
    
    \begin{center}
    \begin{tikzpicture}[
        node distance=1.5cm and 1.5cm,
        box/.style={rectangle, draw=black, thick, fill=blue!10, text width=6cm, align=center, rounded corners, minimum height=1.5cm},
        arrow/.style={->, thick, >=stealth}
    ]
        \node[box, fill=green!10] (input) {Input Narrative Text};
        \node[box] (chunking) [below=1.5cm of input] {Text Chunking \\ (Max 80 words/chunk)};
        
        \node[box, fill=purple!10] (tts) [below left=2cm and 0.5cm of chunking] {\textbf{T5-TTS Synthesis} \\ Generate Speech \\ resample to 48kHz};
        \node[box, fill=orange!10] (ac) [below right=2cm and 0.5cm of chunking] {\textbf{Audio\-Conditioner} \\ Generate Music \\ Match Duration};
        
        \node[box] (mixer) [below=10cm of chunking] {Length Matching \\ \& Dual Mixer ($Gains$)};
        \node[box, fill=yellow!10] (fade) [below=1.5cm of mixer] {Cross-fade Appending};
        \node[box, fill=green!10] (output) [below=1.5cm of fade] {Merged Audio Output};

        \draw[arrow] (input) -- (chunking);
        \draw[arrow] (chunking.south) -- ++(0,-0.8) -| node[above, pos=0.2, font=\small] {Parallel} (tts.north);
        \draw[arrow] (chunking.south) -- ++(0,-0.8) -| node[above, pos=0.2, font=\small] {Pipeline} (ac.north);
        \draw[arrow] (tts.south) |- (mixer.west);
        \draw[arrow] (ac.south) |- (mixer.east);
        \draw[arrow] (mixer) -- (fade);
        \draw[arrow] (fade) -- (output);
    \end{tikzpicture}
    \end{center}
    
    The text is robustly split using natural pauses (punctuation, newlines). For each chunk --- mandated due to the strict \textbf{47-second generation maximum} of the under-the-hood Stable Audio model —, the script runs the T5 text-to-speech engine concurrently with our Music Generation model. Finally, speech and music arrays are zero-padded to match lengths, multiplied by their specific gains, and blended with dynamic crossfades to avoid clipping artifacts.
}

\column{0.5}

\block{\MakeUppercase{Application III: Video Generation \& Orchestration}}{
    Taking the visual modality further, the \texttt{video\_sound.py} application creates animated cinematic clips with a tightly synchronized and responsive musical score from a single still image.
    \vspace{1cm}
    
    \textbf{Parallel Execution Pathway:}
    \vspace{0.5cm}
    \begin{enumerate}
        \item \textbf{Image Animation:} The input image is parsed through the \textbf{Img2VidSD} Model (Stable Video Diffusion pipeline). This produces a smooth, non-static silent video sequence.
        \item \textbf{Image Orchestration:} Simultaneously, the image goes directly into the \textbf{Audio\-Conditioner} model to extract visual semantics and produce a matching audio waveform.
        \item \textbf{Multimodal Merging:} We integrate \textbf{FFmpeg} through subprocesses to automatically compile the generated silent video (\texttt{.mp4}) and the generated audio (\texttt{.wav}), multiplexing them into a single presentation-ready file.
    \end{enumerate}
    
    \begin{center}
    \begin{tikzpicture}[
        node distance=2cm,
        box/.style={rectangle, draw=black, thick, fill=blue!10, text width=6cm, align=center, rounded corners, minimum height=1.5cm},
        imgbox/.style={rectangle, draw=black, thick, fill=gray!20, minimum width=4cm, minimum height=3cm, align=center, font=\itshape},
        arrow/.style={->, thick, >=stealth}
    ]
        
        \node[box, fill=green!10] (img) {\textbf{Source Image}};
        
        \node[box, fill=teal!10] (vid) [below left=1cm and 0.5cm of img] {Stable Video Diffusion \\ (Img2VidSD)};
        \node[box, fill=orange!10] (aud) [below right=1cm and 0.5cm of img] {AudioConditioner};
        
        \node[box] (vf) [below=1.5cm of vid] {Silent output.mp4};
        \node[box] (af) [below=1.5cm of aud] {Sound output.wav};
        
        \node[box, fill=red!10] (ffmpeg) [below right=1cm and -0.5cm of vf] {FFmpeg \\ Multiplexing};
        
        \node[box, fill=green!10] (final) [below=1.5cm of ffmpeg] {Final Synced Video};
        
        \draw[arrow] (img) -- (vid);
        \draw[arrow] (img) -- (aud);
        \draw[arrow] (vid) -- (vf);
        \draw[arrow] (aud) -- (af);
        \draw[arrow] (vf) |- (ffmpeg);
        \draw[arrow] (af) |- (ffmpeg);
        \draw[arrow] (ffmpeg) -- (final);
        
    \end{tikzpicture}
    \end{center}
    
    These applications showcase the great versatility of \textbf{Audio\-Conditioner}, positioning it as a strong foundation for automated scoring, procedural art generation, and immersive multimodal storytelling.
}

\block{\MakeUppercase{If We Had More Time}}{
    Given more time and compute budget, we would have fine-tuned our model using \textbf{Proximal Policy Optimization (PPO)}. By using the CLAP similarity score (between the generated audio and the text prompt) as a reward signal, the model could strictly optimize itself to directly maximize alignment instead of just distilling a Teacher LLM.
    \vspace{0.5cm}
    
    \begin{itemize}
        \item[\color{rouge485}\textbullet] \textbf{The Bottleneck:} In RL algorithms like PPO, the agent needs to continually generate outputs (rollouts) to explore the environment and receive rewards. 
        \item[\color{rouge485}\textbullet] \textbf{Order of Magnitude:} A single audio generation step with \textbf{Stable Audio} takes approximately \textbf{1 minute} to complete.
        \item[\color{bleu303}\textbullet] \textbf{Conclusion:} Gathering enough generation trajectories to meaningfully update the network via PPO would thus require \textbf{weeks of continuous computing time}, making it unfeasible within the scope of this project.
    \end{itemize}
}

\end{columns}
\end{document}
